Energy and the CES production function

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Clean up graphs document. Now everthing we use in the paper is in one section. All other stuff is in a graveyard.

<<setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE>>=
library(EconData)
library(EconModels)
library(dplyr)
library(reshape2)
library(ggplot2)
library(mosaic)
library(xtable)
library(knitr)
library(texreg)
library(tidyr)
library(scales)

@@

<<>>=
leaf_apply(models, function(mod, id) class(mod), class="cesModel")
@

@@

@@

@@

<<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE>>=
leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE>>=
leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE>>=
leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

@@

<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
require(tidyr)
AllOE %>% 
  mutate(split =
           as.character(
             interaction(
               factor(flavor, labels = c("QA", "UA")), 
               factor(nest, 
                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
               sep = ", ",
               lex.order = FALSE ) )
  ) %>%
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  mutate(
    split2 = relevelFactor(
      factor(split), 
      paste( rep(c("UA", "QA"), times = 4 ), 
             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
             sep=", ")
    )
  ) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    alpha = .8, # size=1.0,
    aes(y = elasticity, 
        colour = factor,
        linetype=factor,
        size = factor
    ) ) +
  facet_grid(split2 ~ Country) +
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.9, .9, .6)) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  labs(x="", y="") +
  xy_theme()
@

@@

<<>>=
ReModels <-
  bind_rows(
  leaf_apply(resampleModels, 
             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
             strict.lists = TRUE)
)

>>>>

<<setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE>>=
library(EconData)
library(EconModels)
library(dplyr)
library(reshape2)
library(ggplot2)
library(mosaic)
library(xtable)
library(knitr)
library(texreg)
library(tidyr)
library(scales)
library(tidyr)

@@

%' <<>>=
%' leaf_apply(models, function(mod, id) class(mod), class="cesModel")
%' @

@@

<<ReModels>>=
ReModels <-
  bind_rows(
  leaf_apply(resampleModels, 
             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
             strict.lists = TRUE)
)
@

@@

<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
AllOE %>% 
  mutate(split =
           as.character(
             interaction(
               factor(flavor, labels = c("QA", "UA")), 
               factor(nest, 
                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
               sep = ", ",
               lex.order = FALSE ) )
  ) %>%
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  mutate(
    split2 = relevelFactor(
      factor(split), 
      paste( rep(c("UA", "QA"), times = 4 ), 
             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
             sep=", ")
    )
  ) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    alpha = .8, # size=1.0,
    aes(y = elasticity, 
        colour = factor,
        linetype=factor,
        size = factor
    ) ) +
  facet_grid(split2 ~ Country) +
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.9, .9, .6)) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  labs(x="", y="") +
  xy_theme()
@

@@

<<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

Here is a table of $\alpha$ values. 
These values represent the initial points of the trajectories. 
We no longer use these values. 
Instead, we use the time-dependent values of alpha.
So, this table goes in the graveyard.

@@

@@

<<>>=
